A possibilistic valid-time model

### 2011-12-01 ipmu2012/introduction.tex
More changes, resulting in one less page...

One issue in these attempts at temporal modeling is off course the inherent complexities of the concept of time. Another is the possible inherent imperfection in the description of notions of time. The temporal notion in a sentence like `The Alhambra, which I can see from my room, is a few hundred years old.' contains imperfection caused by the vagueness of the used expression. The temporal notion in a sentence like `The Alhambra was finished somewhere between 1301 A.D. and 1400 A.D.' contains imperfection caused by the inaccuracy in the given temporal notion, though precise boundaries are given. The transition between temporal granularities~\cite{Lin97} is also considered as a source of imprecision in temporal modelling and some proposals consider granularity as the base of the temporal model~\cite{Cru97}.

@@

To allow information systems to cope with these imperfections, many approaches adopt fuzzy sets for the representation of temporal information~\cite{343607,Dubois:jucs_9_9:fuzziness_and_uncertainty_in}. The temporal relations studied by Allen were recently fuzzified by several authors~\cite{ohlbach04,schockaert08}.

Next to the issues in temporal modelling, the addition of time to a relational database~\cite{Dyreson1994} leads to several more practical problems, as the modelling of a time-variant object has an impact on the database consistency. Different models have been proposed \cite{Jensen91,Snodgrass84} that consider time as a crisp notion. In recent works, some authors consider the necessity of allowing imprecision in temporal models~\cite{Cru97,Garrido2009}.

>>>>

One issue in these attempts at temporal modelling is off course the inherent complexities of the concept of time. Another is the possible inherent imperfection in the description of notions of time. The temporal notion in a sentence like `The Alhambra, which I can see from my room, is a few hundred years old.' contains imperfection caused by the vagueness of the used expression. The temporal notion in a sentence like `The Alhambra was finished somewhere between 1301 A.D. and 1400 A.D.' contains imperfection caused by the inaccuracy in the given temporal notion, though precise boundaries are given. The transition between temporal granularities~\cite{Lin97} is also considered as a source of imprecision in temporal modelling and some proposals consider granularity as the base of the temporal model~\cite{Cru97}.

@@

To allow information systems to cope with these imperfections, many approaches adopt fuzzy sets for the representation of temporal information~\cite{Billiet:Pons:Matthe:DeTre:Pons:2011:BipolarFuzzy,Dubois:jucs_9_9:fuzziness_and_uncertainty_in}. The temporal relations studied by Allen were recently fuzzified by several authors~\cite{ohlbach04,schockaert08}.

Next to the issues in temporal modelling, the addition of time to a relational database leads to several more practical problems, as the modelling of a time-variant object has an impact on the database consistency. Different models have been proposed \cite{Jensen91,Snodgrass84,Nascimento95} that consider time as a crisp notion. In recent works, some authors consider the necessity of allowing imprecision in temporal models~\cite{Cru97,Garrido2009}.
